---
title: "R Notebook"
output: html_notebook
---
# Project Euler 112 - bouncy...

Working from left-to-right if no digit is exceeded by the digit to its left it is called an increasing number; for example, 134468.

Similarly if no digit is exceeded by the digit to its right it is called a decreasing number; for example, 66420.

We shall call a positive integer that is neither increasing nor decreasing a "bouncy" number; for example, 155349.

There are a lot of bouncy numbers. There are 525 below 1000. When we get to 538, the proportion of bouncy numbers reaches 50% (for the first time)

When we get to 21780, the proportion reaches 90% (for the first time).

For what number, do we reach 99% bouncy numbers for the first time?

Clearly we will need a function to check if a number is bouncy.

```{r}
bouncy <- function(x){
  digits <- as.numeric(unlist(strsplit(as.character(x),"")))
  return(digits)
}

a <- bouncy(155349)

c <- c(0,a)
c  
```

```{r}
(b <- c(a,0))
b-c
```
hvis position i altid er større end position i-1
