---
title: "Euler 187"
output: html_document
date: '2018-05-28'
params:
  done: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Number of numbers that can be expressed as the product of just two
primes. Below $10^8$


```{r}
library(numbers)
n <- 10**8
numbers <- primes(n)
length(numbers)
```


2 times all the primes below n/2 will give all the semiprimes that have 2 as one 
of the primefactors (smaller than n).

3 times all the primes below n/3 will in the same way give all the semiprimes, 
that have 3 as one of the primefactors.

If I can figure out how many primes there are below n/2, I get the number of semiprimes that has 2 as one of the two primefactors. The same for the number of primes below n/3. If continue 
that to $\sqrt{n}$, and add them all together, I should get the total number of semiprimes below n.

The number of primes below n/2 is:

```{r}
length(numbers[numbers<n/2])
```

And the number of primes below n/3 is:
```{r}
length(numbers[numbers<n/3])
```



I do want to multiply 3 by 3. But I need to exclude 2.

```{r}
length(numbers[numbers<n/3 & numbers>=3])
```


I just need to do it for all of them.

```{r}
n_semi_primes <- function(x){
  counter <- 0
  for(i in numbers[numbers<=sqrt(x)]){
    counter <- counter + length(numbers[numbers<x/i & numbers>=i])
  }
  return(counter)
}

```


Testing:
```{r}
n_semi_primes(30)
```

Getting the answer:
```{r}
answer <- n_semi_primes(10**8)
```


