---
title: "Project Euler 5 - Smallest multiple"
output: html_notebook
---

What is the smallest, positive, number that can be divided by all numbers from 1 to 20 without any remainder?

We are given that 2520 is the smallest that can be divided by all numbers from 1:10.

One number that can definitely be divided by all numbers from 1:20 is:
```{r}
factorial(20)
```

But given that 
```{r}
factorial(10)
```
is rather larger than 2520, it is definitely not the answer.

The answer must be a multiple of all the primes smaller than 20. A number that is divisible by 15, will be divisible by
3 and 5.

The library "numbers" have a lot of useful functions. Primes(20) returns all primes smaller than 20, and prod() returns the product of all those primes

```{r}
library(numbers)
prod(Primes(20))
```

Could that be the answer?

What we are looking at is the modulo-operator. 9699690 modulo 2 - what is the remainder? We know that all the remainders, dividing by 1 to 20 must be 0.
```{r}
prod(Primes(20)) %% 2
```
And our large product is divisible by 2 without a remainder.

Thankfully the operator is vectorized, so we can do all the divisions in one go:
```{r}
9699690 %% 1:20
```

Nope.
```{r}
9699690 %% 4
```

Leaves a remainder.

```{r}
(2*9699690) %% 4
```

Now I just need to find the number to multiply 9699690 with, in order for all the divisions to have a remainder of 0.
That is, change i in this code until the answer is true.
```{r}
i <- 2
all((i*9699690) %% 1:20 == 0)
```

Starting with 1*9699690, I test if all the remainders of the divisions by all numbers from 1 to 20 is zero.
As long as they are not, I increase i by 1, save i*9699690 as the answer, and test again.
If the test is TRUE, that is all the remainders are 0, the while-loop quits, and I have the answer.

```{r}
i <- 1
while(!all((i*9699690) %% 1:20 == 0)){
 i <- i + 1
 answer <- i*9699690
}
```

