---
title: "Euler 14"
output: html_document
date: '2018-02-12'
params:
  done: F
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

We have a starting number n, and calculate the next. 
If n is even, the next number is n/2
If n is odd, the next number is 3n+1

Continuing we will always (although that is not proved), finish at 1.

Which starting number, below 1.000.000 give us the longest chain.

The example is:

13 -> 40 -> 20 -> 10 -> 5 -> 16 -> 8 -> 4 -> 2 -> 1

So, starting with n = 13, we get at chain with length 10.

From that, we can conclude, that if we start with 13, a chain starting with
40, will be shorter. Therefore, there is no reason to test the starting numbers
40, 20, 10, 5, 16, 8, 4, 2 or 1. Because they will all lead to a chain that
is shorter than the chain beginning with 13.

```{r}
as.logical(4%%2)
library(tidyverse)
next_step <- function(n){
  if_else(as.logical(n%%2), 3*n+1, n/2)
}

get_chain <- function(n){
  res <- n
  while(n != 1){
    n <- next_step(res[length(res)])
    res <- c(res, n)}
  res
  }


```

Because of that, we can generate a chain for a given starting number,
and not only get the length, but also eliminate all the numbers in the chain
as possible candiates (except the first in the chain of course)

```{r}
candidates <- data.frame(candidate = 1:1000000, length = 0)

while(nrow(candidates)>1){
  test_value <- sample(candidates[(candidates$length==0),]$candidate, size = 1)
  chain <- get_chain(test_value)
  candidates[candidates$candidate == test_value,2] <- length(chain)
  candidates <- candidates[!(candidates$candidate %in% c(chain[-1],NA)),]
  candidates <- candidates[(!(candidates$length < max(candidates$length))) | (candidates$length ==0), ]
}


```

