---
title: "Euler 5"
author: "Christian Knudsen"
date: "2015-07-23"
output: html_document
params:
  done: T
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Den nedre grænse for svaret er produktet af primtallene under x.

Det beregner vi - og finder de tal i range fra 1 til x, der ikke går op i vores
tentative svar.

Det mindste af de tal i ranget der ikke går op i det foreløbige svar identificeres.

Den laveste primfaktor i det tal ganges på det foreløbige svar, og processen
gentages til alle tal i ranget går op i svaret.

```{r eval  =F}
library(numbers)

answer <- function(x){
  lower <- prod(numbers::Primes(1,x))
  range <- 1:x
  while(!all(lower %% range == 0)){
    kand <- min(range[lower %% range != 0])
    kand <- min(primeFactors(kand)) 
    lower <- lower * kand
  }
  lower
}

answer(20)

```


det er ikke en specielt tilfredsstillende løsning. Den engelske jeg har 
produceret er således::


What is the smallest, positive, number that can be divided by all numbers from 1 to 20 without any remainder?

We are given that 2520 is the smallest that can be divided by all numbers from 1:10.

One number that can definitely be divided by all numbers from 1:20 is:

factorial(20)

## [1] 2.432902e+18


But given that

factorial(10)

## [1] 3628800


is rather larger than 2520, it is definitely not the answer.

The answer must be a multiple of all the primes smaller than 20. A number that is divisible by 15, will be divisible by
3 and 5.

The library “numbers” have a lot of useful functions. Primes(20) returns all primes smaller than 20, and prod() returns the product of all those primes

library(numbers)
prod(Primes(20))

## [1] 9699690


Could that be the answer?

What we are looking at is the modulo-operator. 9699690 modulo 2 - what is the remainder? We know that all the remainders, dividing by 1 to 20 must be 0.

prod(Primes(20)) %% 2

## [1] 0


And our large product is divisible by 2 without a remainder.

Thankfully the operator is vectorized, so we can do all the divisions in one go:

9699690 %% 1:20

##  [1]  0  0  0  2  0  0  0  2  3  0  0  6  0  0  0 10  0 12  0 10


Nope.

9699690 %% 4

## [1] 2


Leaves a remainder.

(2*9699690) %% 4

## [1] 0


Now I just need to find the number to multiply 9699690 with, in order for all the divisions to have a remainder of 0.
That is, change i in this code until the answer is true.

i <- 2
all((i*9699690) %% 1:20 == 0)

## [1] FALSE


Starting with 1*9699690, I test if all the remainders of the divisions by all numbers from 1 to 20 is zero.
As long as they are not, I increase i by 1, save i*9699690 as the answer, and test again.
If the test is TRUE, that is all the remainders are 0, the while-loop quits, and I have the answer.

i <- 1
while(!all((i*9699690) %% 1:20 == 0)){
 i <- i + 1
 answer <- i*9699690
}
