---
title: "Euler 15"
output: html_document
date: '2018-02-06'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In a nxn grid move between the nodes in the grid, starting at the upper-left
corner. Take 1 step either to the right or to the left. How many routes are
there to the bottom right corner.

We are told there are exactly 6 routes in an 2x2 grid.

In that case we need to take exactly 4 steps. Two to the left, and two downwards.

or, l,l,d,d. How many ways can we do that?

That is a permutation, and a formula for handling that exists:

$$ \frac{n!}{k_1!\cdot k_2!\cdot \ldots \dot k_r!} $$

Where n is the total number of elements (4), and $k_r$ is the number of unique
elements r (2 each, $k_1 = 2$ and $k_2 = 2$), and the ! denotes taking the faculty.

Resulting in:
```{r}
factorial(4)/(factorial(2)*factorial(2))
```
Now we are tasked with finding the number of different ways to get from the 
upper-left corner to the lower-right corner in a 20x20 grid.

That translates to the same calculation for n = 40 and $k_1 = k_2 = 20$:

```{r}
answer <- factorial(40)/(factorial(20)*factorial(20))
```
