---
title: "Euler 17"
output: html_document
date: '2018-02-08'
params:
  done: T
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Writing out the numbers 1 to 5 in words give us:
one, two, three, four, five. There are 3 + 3 + 5 + 4 + 4 = 19 letters in total.

If we write out all numbers from 1 to 1000 (inclusive) in words, how many letters
would be used? Note that 342 is written as "three hundred and forty-two" and that
we count "and" but not "-" or " ". 

We could write something on our own. Numbers 1 to 19 are different, but otherwise
there is a system. 20 to 29 is ten times "twenty" and the words "one" to "nine".
When we have all numbers spelled out from 1 to 99, there is repetition. "one hundred and" 
combined with all the numbers from 1 to 99 (remember to add one hundred as itself).

Instead we can load the package `english`, that does that for us:

```{r eval = TRUE}
library(english)
english(999)
```

Now we pour the numbers 1 to 1000 into it (fortunately it is vectorized):

```{r}
all_numbers_as_words <- english(1:1000)
```

We then collapse that to a single string:

```{r}
one_single_string <- paste0(all_numbers_as_words, collapse = "")
```
We do get rid of a lot of the whitespaces. But not all of them. 

```{r}
without_ws <- gsub(" ", "", one_single_string)
```

The hyphens are removed in the same way:

```{r}
without_hyphens <- gsub("-", "", without_ws)
```

And the answer is found by counting the number of characters in the string:

```{r}
answers <- nchar(without_hyphens)
```

