---
title: "Euler 30"
format: html
date: "2018-02-09"
---


The number 1634 can be written as the sum of fourth powers of its digits:

$$1634 = 1^4 + 6^4 + 3^4 + 4^4$$

Identify all numbers that can be written as the sum of their fifth powers of their digits. We do not include 1, as 
1 = 1^5 is not a sum.

Jumping right into it - a (vectorised) function that returns the sum of the fifth powers of the digits. Yes 
it could probably be written in a single line:
```{r}
fifth_sum <- function(number){
    number <- as.character(number)
    number <- lapply(sapply(number, strsplit, ""), as.numeric)
    number <- lapply(number, function(x) x^5)
    lapply(number, sum)
}
```


Where should we stop? The maximum value of a single digit is:

```{r}
9^5
```

If we have a 9 digit number, the maximum sum of the fifth powers of a 9 digit number would be:
```{r}
9*9^5
```

For af 7 digit number it would be:

```{r}
7*9^5
```

This is significantly less than the lowest 7 digit number: No sum of the fifth powers of a 7 digit number will ever
be 7 digits itself.

Whereas a 6 digit numer have a maximum sum of:
```{r}
6*9^5
```

So we do have to check up to and including 6 digit numbers.

Lets do that. Construct a vector with all numbers from 2 to 999999. Calculate the sums, subset the original 
vector, and sum:

```{r}
test <- 2:999999
sums <- fifth_sum(test)
answer <- sum(test[test == sums])
```
