---
title: "Euler 42"
format: html
date: '2018-03-20'
---


A triangle number is given by

$$t_n = \frac{1}{2}n(n+1)$$

We want to determine if a number is triangular.

I have a helperfunction for that:

```{r}
source("helpers.R")
```

It looks like this:

```{r}
is_triangle
```


We can also represent a number as a combination of letters. Or rather the other way around. 

Take each letter, give it the value of its position in the alphabet. Add all values togehter:

ABC -> 1, 2, 3 -> 1 + 2 + 3 =6

Let us also write a function for that:

```{r}
lettervalue <- function(chars){
  chars <- toupper(chars)
  t <- unlist(strsplit(chars,""))
  sum(match(t, LETTERS))
}
```

We now get a list of words. How many of these, converted to a sum with the function above, is a triangle number?

```{r eval = FALSE}
wordlist <- scan("solutions/0042_words.txt", what=character(), sep=",", quiet=TRUE)
```

Neither the `is_triangle` nor `lettervalues` functions are vectorised, so I have to map:

```{r}
library(purrr)

answer <- map_int(wordlist, lettervalue) |> 
  map_lgl(is_triangle) |> 
  sum()
```

