---
title: "Euler 43"
format: html
date: '2018-04-11'
---

All 0:9 pandigital numbers.

Numbering the positions $d_1$ to $d_10$, certain conditions have to be met,
eg $d_2d_3d_4$ have to be divisible by 2. Increasing the "window" the three
digits have to be divisible by the consecutive primes.

Generating all the potential pandigital numbers (as individual numbers)
```{r eval = FALSE}
library(gtools)
test <- permutations(10,10,c(0:9))
```

We now have $d_6$ in column 6. And it needs to be either 0 or 5.

```{r eval = FALSE}
test <- subset(test,test[,6]%in%c(05))
```

$d_4$ needs to be even:

```{r eval = FALSE}
test <- subset(test,test[,4]%in%c(0,2,4,6,8))
```


$d_3d_4_d5$ needs to be divisible by 3:

```{r eval = FALSE}
test <- subset(test,((test[,3]*100+test[,4]*10+test[,5])%%3)==0)
```

$d_5d_6d_7$ must be divisible by 7

```{r eval = FALSE}
test <- subset(test, ((test[,5]*100+test[,6]*10+test[,7])%%7)==0)
```

$d_6d_7d_8$ must be divisible by 11:

```{r eval = FALSE}
test <- subset(test, ((test[,6]*100+test[,7]*10+test[,8])%%11)==0)
```

$d_7d_8d_9$ must be divisible by 13:
```{r eval = FALSE}
test <- subset(test, ((test[,7]*100+test[,8]*10+test[,9])%%13)==0)
```

And finally, $d_8d_9d_10$ must be divisible by 17:

```{r eval = FALSE}
test <- subset(test, ((test[,8]*100+test[,9]*10+test[,10])%%17)==0)
```

Collapse the surviving numbers and convert to numeric:

```{r eval = FALSE}
answer <- sum(as.numeric(apply(test,1,paste, collapse="")))
```
