---
title: "Euler 187"
output: html_document
date: '2018-05-28'
params:
  done: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Number of numbers that can be expressed as the product of just two
primes. Below $10^8$


```{r}
library(numbers)
n <- 10**8
numbers <- primes(n)
length(numbers)
```


2 times all the primes below n/2 will give all the semiprimes that have 2 as one 
of the primefactors (smaller than n).

3 times all the primes below n/3 will in the same way give all the semiprimes, 
that have 3 as one of the primefactors.

If I can figure out how many primes there are below n/2, I get the number of semiprimes that has 2 as one of the two primefactors. The same for the number of primes below n/3. If continue 
that to $\sqrt{n}$, and add them all together, I should get the total number of semiprimes below n.

The number of primes below n/2 is:

```{r}
length(numbers[numbers<n/2])
```

And the number of primes below n/3 is:
```{r}
length(numbers[numbers<n/3])
```



I do want to multiply 3 by 3. But I need to exclude 2.

```{r}
length(numbers[numbers<n/3 & numbers>=3])
```


I just need to do it for all of them.

```{r}
n_semi_primes <- function(x){
  counter <- 0
  for(i in numbers[numbers<=sqrt(x)]){
    counter <- counter + length(numbers[numbers<x/i & numbers>=i])
  }
  return(counter)
}

```


Testing:
```{r}
n_semi_primes(30)
```

Getting the answer:
```{r}
answer <- n_semi_primes(10**8)
```

## Herunder fra nusse.dk

Project Euler 187. Semiprimes

I had to look it up. Semiprimes are numbers that are the product of two prime numbers. And only two, although they may be equal.

There are ten of them below 30: 4, 6, 9, 10, 14, 15, 21, 22, 25 and 26.

16 is not. The only primefactor is 2, but it occurs four times.

How many of these semiprimes are there below 108?

That should be pretty straightforward: Generate all primes below 108, make all the multiplications, and count how many uniqe numbers there are below n, where n=108.

One problem:

n <- 10**8
numbers <- primes(n)
length(numbers)

## [1] 5761455


That is a lot of numbers to multiply.

A trick: 2 times all the primes below n/2 will give all the semiprimes that have 2 as one of the primefactors (smaller than n).

3 times all the primes below n/3 will in the same way give all the semiprimes, that have 3 as one of the primefactors.

If I can figure out how many primes there are below n/2, I get the number of semiprimes that has 2 as one of the two primefactors. The same for the number of primes below n/3. If continue that to \(\sqrt(n)\), and add them all together, I should get the total number of semiprimes below n.

One issue though. The first prime below n/2 that I multiply by 2, is 3. And the first prime below n/3 that I multiply by 3 is 2. Both giving 6. I need to figure out how to only count 6 one time.

I just generated all the primes below n. The number of primes below n/2 is:

length(numbers[numbers<n/2])

## [1] 3001134


And the number of primes below n/3 is:

length(numbers[numbers<n/3])

## [1] 2050943


I do want to multiply 3 by 3. But I need to exclude 2.

length(numbers[numbers<n/3 & numbers>=3])

## [1] 2050942


Qap'la! One less prime.

I just need to do it for all of them.

n_semi_primes <- function(x){
  counter <- 0
  for(i in numbers[numbers<=sqrt(x)]){
    counter <- counter + length(numbers[numbers<x/i & numbers>=i])
  }
  return(counter)
}


I'm writing this as a function, taking a limit x. A counter is set to 0. And for all primes i less than \(\sqrt(n)\), I add the number of primes between i and < x/i.

I can test it on the example given:

n_semi_primes(30)

## [1] 10


That was the number of semiprimes below 30. And then it is just a question of running it on 108:

answer <- n_semi_primes(10**8)

