---
title: "Anagramic squares"
output: html_notebook
---

By replacing each of the letters in the word CARE with 1, 2, 9, and 6 respectively, we form a square number: 1296 = 36^2^. What is remarkable is that, by using the same digital substitutions, the anagram, RACE, also forms a square number: 9216 = 962. We shall call CARE (and RACE) a square anagram word pair and specify further that leading zeroes are not permitted, neither may a different letter have the same digital value as another letter.

Using words.txt (right click and 'Save Link/Target As...'), a 16K text file containing nearly two-thousand common English words, find all the square anagram word pairs (a palindromic word is NOT considered to be an anagram of itself).

What is the largest square number formed by any member of such a pair?

NOTE: All anagrams formed must be contained in the given text file.


Let us begin by getting the words into R:

```{r}
library(readr)
library(tidyverse)
test <- read_csv("p098_words.txt")
test <- colnames(test)
```

Next, I'll need to be able to check if two words are anagrams. If I take two words, and split them into individual letters, sort those letters, and collapse them into a string, then, if those two words are anagrams of each other, the collapsed strings will be identical.

Lets write a vectorized function to take words, and return those ordered words.

```{r}
sort_ana <- function(w){
 require(magrittr)
 require(stringr)
  w  %>%  
    str_split("") %>% 
    lapply(sort) %>% 
    lapply(paste0, collapse="") %>% 
    unlist()
}
```

Let us see what it does, because I dont think the description above was very clear:
```{r}
library(tidyverse)
testing <- c("CARE", "RACE")
sort_ana(testing)
```
See, "CARE" and "RACE" are both converted to the same "word", "ACER". That means that "CARE" and "RACE" are anagrams.

Then I take the list of words, convert them to a tibble, and renames the column (as value).
I make a new variable "ana" that is equal to the sorted words. 
Then I group the tibble by those sorted words, and filter out all groups that have less than 2 words in it. I then ungroup, and sort the tibble by the sorted words.
```{r}
test %>% 
  as.tibble() %>% 
  rename(w = value) %>% 
  mutate(ana = sort_ana(w)) %>% 
  group_by(ana) %>% 
  filter(n()>1) %>% 
  ungroup() %>% 
  arrange(ana)
```

There are the 85 sets of anagrams I need to handle.
Of those are:
```{r}
test %>% 
  as.tibble() %>% 
  rename(w = value) %>% 
  mutate(ana = sort_ana(w)) %>% 
  group_by(ana) %>% 
  filter(n()==2) %>% 
  ungroup() %>% 
  arrange(ana)
```

82 pairs. And:

```{r}
test %>% 
  as.tibble() %>% 
  rename(w = value) %>% 
  mutate(ana = sort_ana(w)) %>% 
  group_by(ana) %>% 
  filter(n()==3) %>% 
  ungroup() %>% 
  arrange(ana)
```

3 a triplet.


The distribution of lengths are:

```{r}
test %>% 
  as.tibble() %>% 
  rename(w = value) %>% 
  mutate(ana = sort_ana(w)) %>% 
  group_by(ana) %>% 
  filter(n()>1) %>% 
  ungroup() %>% 
  mutate(len = nchar(ana)) %$% 
  table(len)
```

I will have to find the highest square. If I begin with the longest words, I will probably not have to worry about the triplet "POST/STOP/SPOT"

The squares I need to handle are not going to be longer than 9 digits. Or, no squares that are larger than:
```{r}
sqrt(999999999)
```
Squared.

The list of possible squares can then be constructed:
```{r}
squares <- (1:31622)**2
  
```

I'll probably need to be able to filter that list based on how many digits the numbers have. Lets write a function for that:

```{r}
ndigits <- function(i){
  floor(log10(i))+1
}
```


Lets look at the word "CAT", and the three digit square 169. How do I map those two?

I start by splitting the word and the number in individual letters and digits.

```{r}
w <- "CAT"
(w <- unlist(str_split(w,"")))

n <- 169
(n <- unlist(str_split(as.character(n),"")))


```

I take the first letter of the word, and get the positions of that letter in the word. 

```{r}
w %in% w[1]
```

Then I get the digits in the number, that corresponds to those positions:
```{r}
n[w %in% w[1]]
```

Those digits should be the same. If not, the C, that matches 1 in position 1, matches a different digit later in the word. And then the word cannot be matched correctly to the number, and the result would be false.

```{r}
if(!all(n[w %in% w[1]] == n[1])){res <- FALSE}
```

I'm not quite sure it is necessary, but I then do the same check, just reversed:
```{r}
if(!all(w[n %in% n[1]] == w[1])){res <- FALSE}
```

And of course I need to do that for all letters, not just the first. That translates into this function:

```{r}
map_pos <- function(w, n){
  w <- trimws(w)
  w <- unlist(str_split(w,""))
  n <- unlist(str_split(as.character(n),""))
  res <- TRUE
  for(i in 1:length(w)){
    if(!all(n[w %in% w[i]] == n[i])){res <- FALSE}
    if(!all(w[n %in% n[i]] == w[i])){res <- FALSE}
  }
  return(res)
}

```

Yes, I know I should check if the word and the number is the same lenght. I'm too lazy to do that here.

Now I have a way to check if a given combination of word and number can be matched correctly. I can just try every combination, and keep the ones that are true.

Next I will have to take such a combination, and apply the mapping to a new word, in order to get a new number. 
I begin by making sure that the original word, w, is a character, and any whitespace is trimmed.
The same goes for the new word, nw, that I want to map to a new number.

Then both words and the number is split into individual letters and digits. And an new number vector, nn, is initialized.

At the moment of writing I'm a bit tired. So excuse any lack of clarity. But for each position in the length of the words (again, I should, but dont, check that the words are of equal length), I extract the letter in the new word, use that letter as a name in the vector containing the original number, and add that to the vector containing the new number I'm trying to generate.

When I have done that for the entire length, I have a vector that I can collapse, coerce as numeric, and return.
```{r}
map_tal <- function(w, n, nw){
  w <- as.character(w)
  w <- as.character(nytord)
  w <- trimws(w)
  nw <- trimws(nw)
  w <- unlist(str_split(w,""))
  n <- unlist(str_split(as.character(n),""))
  nw <- unlist(str_split(nw,""))
  nn <- numeric(length(nw))
  names(w) <- n
  names(n) <- w
  for(k in 1:length(w)){
    nn[k] <- n[nw[k]]
  }
  nn <- str_c(nn, collapse="")
  nn <- as.numeric(nn)
  return(nn)
}
```





```{r}
kandidater <- test %>% 
  as.tibble() %>% 
  rename(w = value) %>% 
  mutate(ana = sort_ana(w)) %>% 
  group_by(ana) %>% 
  filter(n()>1) %>% 
  group_by(ana) %>% 
  summarise(ord = paste(w, collapse=", ")) %>% 
  separate(ord, into=c("ord1", "ord2", "ord3"), sep=",")
kandidater
```



der er par og firs par. og en enkelt triplet.

mathblog skriver at det længste er på 8 karakterer. Det passer ikke, det er på 9. Introduce og reduction

Nå. Det første ord i parret testes mod hver eneste kvadrattal. Der hvor tallet kan matches med et kvadrattal, skal jeg teste om det andet ord i parret, når det konverteres efter det mønster vi har fra det første tal - også er et kvadrattal. Det største af de tal der kan bruges gemmes.

Nå. Vi tager nu kandidatlisten. Og får tilføjet en længde:
```{r}
kandidater <- kandidater %>% 
  mutate(len = nchar(ord1)) %>% 
  select(ord1, ord2, len)
```

Jeg antager at det ord vi søger, er længere end 4. Så det er lige meget med tripletten.

```{r}
l <- 5
options(scipen = 42)

mulige_ord <- kandidater %>% 
  filter(len==l)

mulige_tal <- kvadrater[ndigits(kvadrater)==l]


for(i in 1:nrow(mulige_ord)){
  for(j in 1:length(mulige_tal)){
    if(map_pos(mulige_ord[i,1],mulige_tal[j])){
        if(map_tal(mulige_ord[i,1], mulige_tal[j], mulige_ord[i,2]) %in% mulige_tal){
          print(paste(mulige_ord[i,1], mulige_tal[j], mulige_ord[i,2],map_tal(mulige_ord[i,1], mulige_tal[j], mulige_ord[i,2]), sep=" "))}
        
    }
  }
  
}
i <- 2
j <- 149


map_tal("BOARD", 12769, "BROAD")

View(mulige_ord)
mulige_ord[i,1]
mulige_ord[i,2]
mulige_tal[j]
map_tal(mulige_ord[i,1], mulige_tal[j], mulige_ord[i,2])

as.character(mulige_ord[i,1] )
mulige_tal[j]
mulige_ord[i,2]

61504
str(map_tal("PHASE", 61504, "SHAPE") )
mulige_tal[j]
mulige_ord[i,1]

1+1
```

